%Mega Man X
\chapter{X}\label{char:X}
X is the main protagonist of the Mega Man series which bares his names. He is the last creation of the brilliant Dr.~Light, a robot built with the gift of free will and limitless potential, and a Maverick Haunter appointed of stopping reploids gone maverick to hurt human people. 
X's primary characteristic is his kind heart and peaceful attitude, which makes him repel violence, often trying to reason with his enemies. However despite this attitude X know well the threat mavericks are and, even if unwilling, fight against them with all his strength to bring the world at peace.

\section{Technical Specifications}
X's specification can be found both in the opening scene of the first Mega Man X game and in the \emph{Rockman \& Rockman X Daizukan}~\cite{book:RRXD}-\cite{X_specs_translated} book. While some information overlap between these sources other are exclusive to a single one, hence here both of them are reported as source of information.

\paragraph{General Information}
\begin{itemize}
	\item Height: 160 cm.
	\item Weight: 57 Kg (lighter than Rock due technological improvements).
	\item Main energy source is Solar energy.
	\item Armor is composed by a lightweight ``Titanium-X'' alloy, the strongest metal in the world. Very light and resistant to heat and shots.
	\item Internal skeleton is a super elastic armor that can reduce received damage by approximately 93\%.
	\item A.I. age between 14 and 15 years old in human terms at the beginning of the first game. Matures as time passes.
\end{itemize}

\paragraph{Head equipment}
\begin{itemize}
	\item Eyes are constituted by broad-range cameras, giving him the ability to see more things human eye can.
	\item Ears are composed by ulta-high sound recognition system, allowing to hear even ultrasonic sounds.
	\item Voice is produced by a voice generation system made by HAYATOM Inc. (MOKUOO Inc. in Japanese version). 
\end{itemize}

\paragraph{Chest equipment}
\begin{itemize}
	\item An Accumulative Energy Generation Device allow to accumulate solar energy and provide X with the sufficient amount of power required to work.
	\item A Micro-fusion fuel tank, which stores fuel for X to use when solar energy is not available, such as caves or underwater.
	\item The Central Joint-controlling system, X's secondary brain which control his movements.
\end{itemize}

\paragraph{Leg equipment}
\begin{itemize}
	\item Gyroscopic Stabilization System/Full auto-balancer helps X in remaining stabilized and land properly from any state he's in.
	\item The Emergency Acceleration System, which enables X to accelerate at high speed in a short amount of time. This equipment is optional and must be installed in a second moment.
\end{itemize}

\paragraph{Arm equipment}
\begin{itemize}
	\item Mega Buster Mk.17 (X-Buster). X’s basic weapon built into his hand. When fighting his hand retracts and leave the place to the buster~\cite{elysium_weapons}
	\item Energy Amplifier to store and concentrate energy into a more powerful shot, the Charged Shot.
	\item Variable Weapon system: Allow the X-buster to transform and emulate attack from enemies bosses. How the copy/learning process is performed remains, however, unknown.
\end{itemize}


\section{Creation}
X's creation begins in the year 20XX by the hand of famous scientist Dr.~Thomas Light. Reasons that brought Dr.~Light are to be found into two main facts that happened during the scientist's life. The first one was the coming of an unknown computer virus from space that caused robots to go violent (which could be a reference both to the ``Evil energy'' appeared in \emph{Mega Man 8} or the \textit{Roboenza} Virus appeared in \emph{Mega Man 10}). After this event Dr.~Light decides that a new battle robot had to be created in order to protect the future of earth~\cite{mega_man_network:Zero_timeline}, and starts building X. On why creating X and not upgrade Rock, the original \textit{Mega Man}, many option can be formulated, one being the fact that Rock was originally designed to help with laboratory work and not to fight, hence the preference to create a new robot, instead altering Rock too much. In addition since the new robot to be created may fight robot infected with viruses, a new anti-virus system had to be created within him. This last statement fits perfectly with the second reason Dr.~Light began creating X, which is his dream to create a robot who could choose his own path in life, effectively having free will. How it is possible to see from his journal~\cite{Dr.Light_journal}, in fact, the idea of a free-will was born and stayed in him from shortly after events of the first \textit{Mega Man} game up until X's creation, as he believed it was his duty to accomplish such achievement\footnote{\textit{If a robot posses the intelligence to be conscious of the possibility of opposing a human for the right reasons, will it be possible for them to worry aver what path is right? [...] I can sincerely feel that coming to think of this is my duty.} Dr.~Light's journal, 29 March 2017}. Furthermore as Roll herself pointed to Light, free will also create the perfect anti-virus system, as would made impossible for a robot to be manipulated\footnote{\textit{``If artificial intelligence can be aware of its own intelligence, then one can fix any kind of tampering'' [...] However if that very kind of electronic intelligence can realize ideas like hers} (Roll) \textit{, then I think it's possible to establish a consciousness that cannot be manipulated} Dr.~Light's journal, 7 March 2017}.  It is unknown how long it took for Dr.~Light to complete X but, observing from flashbacks shown in the \emph{Day of $\Sigma$} OVA, it is possible to imagine that the development took most of Light's remaining lifetime as flashbacks shown a doctor growing older and weaker as time passes.  During this time period however Light realizes the importance of his project and its impact it could have on the world, due the power X holds, making him also realize the danger X could represent if, should the world turn against him, he takes a wrong path in life or begin to question the firs law of robotics risking disasters even worse than ones created in Wily's incidents~\cite{elysium_light_warning}. To avoid this situation, while still believing in X's good heart (as seen in X's flashback in \emph{Day of $\Sigma$}), Dr.~Light decides that X's moral integrity has to be tested deeply before letting him free. According to his studies, Dr.~Light estimates that about thirty years of testing should be necessaries to completely ensure X's safety, time far beyond his own lifespan. For this reason, being near the end of his life and not having anyone who could continue his work, Dr.~Light decides creates a special capsule for X to rest in, capable of performing test without the need of someone supervising it while also ensuring X's safety. After giving X farewell, on date 19$^{th}$ September 20XX, Dr.~Light proceeds to seal him away and leaves a message (written or recorded depending on the game) for whoever will find the capsule, explaining who X is and why he's special.

\section{Awakening and birth of reploids}
X's sleep last for about hundred years inside Dr.~Light's laboratory, buried underground and hidden from everything, until Dr.~Cain, a scientist of 21XX, while searching for plant fossils  from Mesozoic (or preserved plant from Middle Age~\cite{elysium_Cain_journal} in the Japnese version) randomly finds the laboratory. After some digging he manages to get in, where he first finds Light's note and documentation relative to X and, the following day, X's capsule itself still working. After reading Light's last note and warning message, and checking the capsule status, which as stated in the journal show all indicator on green, on the 14$^{th}$ April 21XX Dr.~Cain awakes X from his slumber. Immediately after meeting him, Cain realizes how incredible X is and how futuristic Light's creation  is, even to his times, and decides to bring X, along all Light's design note, to his laboratory in order to try replicate X's design and create a similar robot.

More than six month were needed to complete the first robot, but on the 22$^{nd}$ November Dr.~Cain manages to create a robot using Light's schematics and X as reference. This new robot, just like X, is fully capable of making decision on his own, even arriving to argue with Cain himself, to his surprise. However the new robot created isn't a perfect copy, as part of X's design couldn't be analyze even with modern technologies forcing Dr.~Cain to fix missing elements at his best, especially components constituting his ``\emph{Distress Circuit}''\cite{book:RMZ_Complete_works} which allows X to choose his side in society, and the new robot's moral integrity of the wasn't test deeply as X's one. However since these difference seems to cause no problems, Dr.~Cain decided to start mass production of these new kind of revolutionary robot, which he named ``\emph{Reploids}''  (or \emph{Repliroids}).

It took not so long for reploids to integrate inside the society as Dr.~Cain himself note in his diary in an entry dated 3$^{rd}$ May, where he states that \textit{everyone seems to be happy to accept them}. Reploids in fact began to work in place of and together with humans in all kind of jobs, especially more dangerous ones which could put humans life at risk. However the situation won't last long,  as first mavericks will shortly start to appears.

\section{Mavericks and Maverick Haunters}

In the following entry in Cain's journal dated 16 July the scientist states: ``\textit{Three reploids went "maverick" today and injured two people before they were stopped. This is the third instance of this type of behavior and I still have no idea of what is causing it!}''. This entry describe first mavericks occurrence in the series although, at the time the entry is written, they look more like isolated events related to some sort of explainable fault. However due the problem mavericks had caused, even with such a small number of occurrences (only three), the journal describes how the idea of halting the production already began to spread, but considering how society now depends on reploids, this idea is discarded from becoming reality. Instead a special organization called ``Haunters'' was established in order to track down and halt mavericks before they cause any damage. Appointed leader of the organization is Sigma, Cain's latest and finest work equipped with last-design circuit which should prevent him from any fault, which also serves as leader of the 17th elite unit, operating on front lines against the maverick threat. X will join the organization only later in time (see \PtIIWarning), where will be assigned to the 17th unit under Sigma and where he will meet his future partner, Zero. 

Thanks to haunters' effort any further injure occurred as consequence of maverick attack, creating a situation of peace that lasted  for almost two years (two month in the English, see \PtIIWarning) During this period X fights together with his commander Sigma, his partner Zero and all his companions against mavericks, but deep inside he keeps questioning about his place in life and the path he has to choose\footnote{``\textit{I am a little worried about X. He seems unsure of his place in life and what Dr. Light had planned for him}'' Journal of Dr.~Cain, 10$^{th}$ December 21XX}.

\section{The X saga and the Maverick Wars}
On 4$^{th}$ July 21XX, Dr.~Cain worst nightmare becomes true. On this day Sigma go maverick and begins his revolution against humanity, which he now considers an obstacle to Reploids evolution that has to be eliminated. Together with him sides most of his subordinates Maverick Haunters longing to follow their leader as well as other reploids seduced by Sigma's charisma and strength. In truth Sigma went maverick long before the day he announced his revolution, as he managed to accurately plan his actions and gathered allies for long time. The only difference between Sigma and any other maverick before him is the fact that while any other reploid, as it goes maverick, goes rampage immediately attacking everyone around him, Sigma instead has had a slow conversion which twisted his sight of the world. Further details on Sigma's conversion will be given in future section of this document, while for the moment it is important to underline Sigma's difference with any other maverick that has appeared until this point in time. After rebellion's beginning, the few Haunters remained loyal to their original purpose, X and Zero Included, begin their counterattack. starting a period of wars which in future will be labeled as ``\emph{Maverick wars}''. 

From now on X's story follows the game's plot. During the event of the first game (and its remake) Zero is appointed as leader of the Maverick Haunters, as being the highest in rank still on the right side, and lead other haunter, X included, in fighting. Zero then asks  X to take care of Sigma's subordinate both because their action are causing trouble to humans and other reploids, but most importantly to allow X to grow up and become stronger,as Sigma is still to powerful for him. Once X disposes of the eight mavericks, Zero contact him to ask help to infiltrate Sigma's fortress, which he managed to locate in the meanwhile. Once inside the two first challenge Vile, which result in his death but in Zero's death too. Finally X face Sigma and defeat him, halting his plans of human extinction. After escaping Sigma's collapsing fortress, X return to the Maverick Haunter headquarters, where he becomes the new leader in charge.
