%Timeline.tex
Here a timeline of all events concerning the Mega Man X series in chronological order. Events which happen at a precise date have it clarified on the right.
\warningbox{\label{time_assumptions}\small{
		\textcolor{red}{This is a only a plausible recreation.}
		Since most of the events presented here don't have a precise date, the order they're placed is only according to the writer's preference. Any other decision about event's ordering has been taken according to \PtIIWarning, or will be explicitly addressed.
}}

\begin{tabularx}{\linewidth}{l X}
	
	\toprule
	\rowcolor{Aquamarine}
	%
	% 20XX
	%
	\multicolumn{2}{c}{\textbf{20XX}}\\
	\addlinespace[1.5ex]
	\tabdot&29$^{th}$ March 20XX: Dr.~Thomas Light begins pondering the idea of a robot capable of choosing his own path in life. \\
	\tabdot& Dr.~Light begins to construct X.\\
	\tabdot& Dr.~Wily begins the construction of Zero, using Rock's and Proto Man's schematics. The objective is to create a robot capable of surpassing both Rock and Bass.\\
	\tabdot& Dr.~Wily finishes to build Zero, but the robot is uncontrollable and attacks everything in sight. Wily decides to seal him away and begins working on a way to correct Zero's behavior.\\
	\tabdot& Dr.~Light finishes to build X, but seals him away in a capsule which can run the thirty-years required tests in autonomy. He then leaves a warning message for whoever will find X.\\
	\tabdot& Dr.~Light dies. His consciousness, however, lives on inside and AI which continue to work on the X project developing the First Armor.\\
	\tabdot& Dr.~Wily completes the Robot Destroy Program, a virus tasked to correct Zero's behavior, and seals it inside Zero's capsule.\\
	\tabdot& Dr.~Wily dies. His consciousness manages however to live on.\\
	\tabdot& The Batton M-501 mechaniloid series is discontinued, in favor of the newer Batton Bone one.\\
	
	%
	% 21XX
	%
	\midrule
	\rowcolor{Aquamarine}
	\multicolumn{2}{c}{\textbf{21XX}}\\
	\addlinespace[1.5ex]
	\tabdot& The Met series is upgraded with the introduction of Metall C-15.\\
	\tabdot&10$^{th}$ April 21XX: Dr.~Cain accidentally finds Dr.~Light's laboratory buried underground while in a archaeological expedition.\\
	\tabdot&13$^{th}$ April 21XX: Dr.~Cain finds X's capsule.\\ 
	\tabdot& 14$^{th} $April 21XX: X awakens.\\
	\tabdot& 15$^{th}$ April 21XX: Dr.~Cain, alongside X and Light's schematics, moves to his laboratory in order to try to create a new type of robot following Dr.~Light's designs.\\
	\tabdot& 22$^{nd}$ November 21XX: Dr.~Cain completes his first reploid.\\
	\tabdot& Cain Industries begin reploids' mass production.\\
	\tabdot& The first instance of a reploid going maverick occurs.\\
	\tabdot& Cain creates Sigma, a strong reploid equipped with last-design brain circuits.\\
	\tabdot& 20$^{th}$ November 21XX: The Council decides to set up a special organization, named ``Maverick Hunters'' with the specific task to hunt down and stop mavericks. Sigma is appointed as the leader.\\
	\tabline& $\cdot$ Sigma is appointed leader of the 17th Elite unit.\\
	\tabline& $\cdot$ Launch Octopus, Wheel Gator and Bubble Crab join the 6th Fleet.\\
	\tabline& $\cdot$ Chill Penguin joins the 13th Polar Division, stationed in the South Pole.\\
	\tabline& $\cdot$ Armored Armadillo is appointed commander of the 8th armored force.\\
	\tabline& $\cdot$ Flame Mammoth becomes captain of the 4th Land Unit stationed in the Middle East.\\
	\tabline& $\cdot$ Storm Eagle becomes leader of the 7th Airborne Unit. Overdrive Ostrich joins the same unit.\\
	\timemoment{Storm Eagle and Storm Owl become friends.}
	\timemoment{Someone mistakes Storm Owl for a penguin, resulting in him developing a grudge against Chill Penguin}
	\timemoment{Magma Dragoon joins the 14th Maverick Hunter special unit, also known as ``grapple unit''}
	\tabline& $\cdot$ Boomer Kuwanger, Gravity Beetle, Flame Stag and Spark Mandrill join the 17th Elite Unit.\\
	\tabline& $\cdot$ Sting Chameleon is assigned to the 9th Special Force (Ranger Unit).\\
	\tabline& $\cdot$ Magna Centipede and Blast Hornet join the 0th Special Unit ``Shinobi''.\\
	\tabline& $\cdot$ Vile joins the 17th Elite Unit\footnote{Here the fact that all mavericks joins the organization from the beginning is only author's flavor as no information about these events are given.}.\\
	\timepoint{Scientists build Crush Crawfish as a combat reploid. However a bug in his AI makes him incredibly violent, and he is sealed away in a warehouse for later repair.}
	\timepoint{Split Mushroom is created as the administrator of the Bio Laboratory}
	\midrule
	\tabdot& 10$^{th}$ December 21XX: Maverick Hunters have been operating for about two years. X is still seeking his place in life.\\
	\timepoint{The Bio Laboratory is shut down, and Split Mushroom is deactivated.}
	\tabdot& Overdrive Ostrich has an accident, which deprives him of his flight ability. Ostrich retires from the Hunters.\\
	\timepoint{Zero's capsule is found, and Zero awakened. He proceeds to kill everyone who draws near.}
	\timemoment{Maverick Hunter's Gamma unit is sent to deal with the ``red maverick'', but all members are ultimately killed.}
	\timemoment{Sigma challenges Zero, but is defeated. However, Zero begins to act weird due to the virus' reprogramming, and Sigma manages to knock him down.}
	\timemoment{Dr.~Cain studies Zero, discovering he can not fully analyze his technology, much like X's.}
	\timepoint{Zero awakens  and joins the 17th Elite Unit}
	\tabdot& X joins the 17th Elite Unit.\\
	\tabdot& Wheel Gator attacks a comrade, and is forced to leave the Hunters becoming a fugitive.\\
	\tabdot& Sigma begins to actuate his plans.\\
	\tabdot& A fault in Vile's brain circuits makes him unstable and borderline-maverick. The high ranks of the Maverick Hunters decides to jail him waiting for a judgment.\\
	\tabdot& Sigma calls back Chill Penguin from the South Pole, making him temporarily join the 17th Elite unit. Before coming back, Chill Penguin eliminates his former superior.\\
	\tabline& $\cdot$ Flame Mammoth is recalled too, but he doesn't join the 17th Elite Unit.\\
	\tabdot&Sigma reaches for Morph Moth, being interested in his powers, and enrolls him into his army. \\
	%
	% day of sigma
	%
	\midrule
	\rowcolor{Aquamarine}
	\multicolumn{2}{c}{\textbf{Day of $\Sigma$ and beginning of the war}}\\
	\addlinespace[1.5ex]
	\tabdot& Vile is arrested, suspected of being a maverick.\\
	\tabdot& Sigma frees Vile, asking him to take care of X.\\
	\tabdot& 4$^{th}$ July 21XX: Sigma attacks a missile base. X and Zero try to stop him, but they fail. Sigma fires missiles onto Abel City, effectively starting the war. During the fight X hit Sigma, causing him scars onto his eyes.\\
	\tabdot& Storm Eagle and his troops attack Sigma, trying to take him down. Sigma wins, putting him under his rule. Storm Eagle is then entrusted with the control of the Death Rogumer.\\
	\tabdot& Sigma's subordinate conquer various strategic points.\\
	\tabline& $\cdot$ Launch Octopus sets up a base in the ocean, to cut down naval transports. Bubble Crab defects too, but remains in the rears.\\
	\tabline& $\cdot$ Chill Penguin occupies a base in a nearby mountain to cause avalanches on the city.\\
	\tabline& $\cdot$ Flame Mammoth occupies a factory and converts it for mass producing weapons needed for the war. However none of his subordinates follow him due his bad attitude as commander.\\
	\tabline& $\cdot$ Boomer Kuwanger captures the tower symbol of Abel city.\\
	\tabline& $\cdot$ Flame Stag disappears after defecting alongside Kuwanger.\\
	\tabline& $\cdot$ Spark Mandrill seizes the power plant, to redirect electricity onto Sigma's facility.\\
	\tabline& $\cdot$ Sting Chameleon occupies a front-line base set inside the forest.\\
	\tabline& $\cdot$ Sigma recalls Overdrive Ostrich, praising him for his remaining abilities. Ostrich pledge his loyalty to Sigma, but remains in the rears.\\
	\tabdot& Sigma sets up his fortress where he leads the operations.\\
	\tabline& $\cdot$ Scientists create Bospider to be a large-scale crusher with an invincible body, but a mistake causes its core to expose after a shock. Sigma decides to use it as guardian to his fortress.\\
	\tabline& $\cdot$ Rangda Bangda is created to crush enemies who enter Sigma's fortress.\\
	\tabline& $\cdot$ Scientists begin the construction of a giant dinosaur-based mechaniloid and a wolf-based mechaniloid capable to combine with Sigma to further enhance his power.\\
	\tabdot& Zero is appointed as leader of the 17th Elite unit and of the entire Haunter organization, being the highest in rank remained to oppose Sigma.\\
	%
	% X1
	%
	\midrule
	\rowcolor{Aquamarine}
	\multicolumn{2}{c}{\textbf{Mega Man X}}\\
	\addlinespace[1.5ex]
	\tabdot& Sigma's troops launch an attack on Abel city's highway. X intervenes to stop the fight.\\
	\tabline& $\cdot$ Vile attacks X on the highway, but Zero's intervention forces him to retreat. In the battle his ride armor is damaged.\\
	\tabdot& Zero entrusts X with dealing with the eight mavericks. Meanwhile he starts searching for Sigma's hideout.\\
	\tabdot& Magna Centipede is captured by the Mavericks, and brainwashed into a loyal soldier.\\
	\tabdot& X manages to defeat all eight mavericks that were threatening Abel city. In the meanwhile he also find capsules from which Dr.~Light AI gives him the first armor pieces.\\
	\timemoment{Gravity Beetle swears revenge against X for his brother's (Boomer Kuwanger) death.}
	\timemoment{Storm Owl develop a grudge against X for killing Storm Owl.}
	\tabdot& Vile repairs and upgrades his ride armor, while also setting up a plan to take down both Zero and X.\\
	\tabline& $\cdot$ Sigma recovers defeated mavericks' dead bodies and resurrect them as an additional line of defense for his fortress.\\
	\tabdot& Zero finds Sigma's hideout, and asks X to reach him to begin the final assault.\\
	\tabdot& X and Zero enter Sigma's fortress but are ambushed by Vile, who captures both of them. However both Zero and X manage to break free from their prison and to take down Vile. Zero, however, also dies in the fight.\\
	\tabdot& X continues traveling through the fortress. Scientists, worried, accelerate the development of the tyrannosaurus mechaniloid mounting its head onto a moving platform, thus creating D-REX, which is however destroyed by X.\\
	%	\tabdot& Sigma manages to separate his mind from the body. His mind flee, while his original body remains back to fight X.\\
	\tabdot& X finally reaches Sigma, and the two fight. X defeats Velguarder first and Sigma immediately after. Sigma decides then to combine himself with the still incomplete wolf-mechaniloid built for him and become Wolf Sigma. X, however, manages to destroy him again. After Sigma's defeat, his fortress begins to collapse and falls into the ocean. X teleports outside.\\
	\tabdot& Sigma's mind separates from the body, surviving the clash with X.\\
	\midrule
	
	%
	% X1 - X2
	%
	\rowcolor{Aquamarine}
	\multicolumn{2}{c}{\textbf{Between X1 and X2}}\\
	\addlinespace[1.5ex]
	\timepoint{X returns the First Armor to Dr.~Light. The data acquired from the fights are used by Light's AI to upgrade the armor.}
	\tabdot& X is appointed leader of the 17th Elite Unit.\\
	\tabdot& Zero's control circuit is retrieved by the maverick hunters form the remaining of Sigma's fortress.\\
	\tabdot& The X-Hunters, led by Serges, emerge from the shadows and take control of Sigma's army.\\
	\timepoint{Zero's body remains are retrieved by the maverick forces. Serges begins its reconstruction. In the same occasion, Vile's remains are also retrieved.}
	\tabdot& To increase the size of their army, the X-Hunters set up different factories to mass-produce Mavericks.\\
	\timemoment{In one of these factories, Wire Sponge is created. Despite his childish attitude, he is enrolled in the mavericks army due his strength.}
	\tabdot& Crystal Snail, a mysterious reploid, is enrolled in Sigma's army.\\
	\tabline& $\cdot$ Wheel Gator reaches the Maverick army, hoping to satisfy his destructive impulses.\\
	\tabdot& Serges begins to build a new body for Sigma.\\
	\tabdot& The battle between Maverick Hunter and Mavericks continues, with heavy losses from both sides.\\
	\timepoint{The Batton Bone series is upgraded to the G-type model}
	\tabdot& Several Maverick Hunters bases are attacked and destroyed, one of them by Violent alone. The total number of effective in the Maverick Hunters organization is reduced to a quarter of its original value.\\
	\timepoint{Following the surge in mavericks attack, Repliforce is created with the task to assist Maverick Hunters. General is appointed as the supreme commander.\footnote{No information about when in time Repliforce is founded. This choice is completely arbitrary and based on the fact that, in X4, we see the v3 version, meaning Repliforce must be running for some time before that point.}}
	\timemoment{Slash Beast joins Repliforce as a soldier to satisfy his feral impulses.}
	\timemoment{Jet Stingray joins Repliforce as well.}
	\timemoment{Frost Walrus is marked as maverick for his destructive impulses and destined to disposal. General steps in, making Walrus join Repliforce.}
	\timemoment{Storm Owl joins Repliforce.}
	\tabdot& Studying the defeated mavericks, Dr.~Cain discovers a chip in reploids brain which causes them to go maverick. The chip bears Sigma's insignia.\\
	\timepoint{Zero's reconstruction is almost finished. However his control circuit is still missing.}
	\tabdot& After some investigations, the maverick hunters locate the factory responsible for creating mavericks. X and his unit are dispatched to destroy the facility. In total six months have been passed since the end of the first uprising.\\
	%%
	% X2
	%%
	\rowcolor{Aquamarine}
	\multicolumn{2}{c}{\textbf{Mega Man X2}}\\
	\addlinespace[1.5ex]
	\tabdot & X destroys the maverick factory, where an army of giant mechaniloid CF-0 were being constructed.\\
	\tabdot & The destruction of the facility slows down X-Hunter's plan. To mitigate such problem, the X-Hunters releases their eight SA-class Mavericks to wreak havoc, hoping to gain enough time to complete their schemes.\\
	\tabline& $\cdot$ Wire Sponge is released inside the Weather Control facility, where he starts playing around with its controls, changing the nearby weather.\\
	\timemoment{Morph Moth is deployed in the scrapyard, to create new mavericks out of scrap.}
	\timemoment{Flame Stag reappears, and conquers a volcano aiming to cause an eruption to cover the sky and begin a new ice age.}
	\timemoment{Magna Centipede conquers the central computer, and from there begins to spread the Maverick Virus around the world.}
	\timemoment{Overdrive Ostrich conquers an abandoned missile base in the desert, aiming to use the remaining missiles to destroy the Maverick Hunters HQ.}
	\timemoment{Bubble Crab is dispatched to defend an underwater base used to ship mavericks around the world.}
	\timemoment{Wheel Gator leads the giant Dinosaur Tank aircraft carrier into a city, to wipe it out.}
	\timemoment{Crystal Snail is sent into the energen mines, to dig out crystals used to generate energy.}
	\timepoint{X destroys two of the SA-class Maverick quicker than expected. The three X-Hunters are forced to take action challenging X to a duel, using Zero's repaired parts as bait.}
	\timepoint{X fights against the three X-Hunters and wins, delivering Zero's parts to Dr.~Cain, who immediately begins his reconstruction.}
	\timepoint{Deprived of their main weapon, Serges hurry in completing Sigma's body. To mitigate the loss of Zero, he also creates a replica of him, loyal to Sigma and with a black armor.}
	\timepoint{X manages to stop all remaining mavericks. In the meanwhile, he also obtains the Second Armor from Dr.~Light capsules.}
	\timepoint{Dr.~Cain manages to locate the X-Hunters fortress, situated in the north pole.}
	\timepoint{Serges completes both Sigma's body and fake Zero.}
	\timemoment{Sigma learns from Serges about Zero's true origins.}
	\timepoint{X storms the X-Hunters base. The three X-Hunters try to stop him using all their available tools, but are destroyed}
	\timemoment{After X-Hunters' defeat, Sigma reveals himself to X, and gives him an appointment to the Central Computer. After the message the base explodes.}
	\timepoint{X meet with Sigma at the Central Computer. Sigma uses the Zero replica to attack X, but the real Zero arrives and destroys his copy.}
	\timemoment{Zero proceeds to destroy the main computer.}
	\timemoment{X and Sigma clashes. X destroys Sigma's new body. Sigma assumes his true form of a virus, and materializes to try killing X. X however manages to defeat him and forces Sigma to flee.}
	%%
	% X2-X3
	%%
	\rowcolor{Aquamarine}
	\multicolumn{2}{c}{\textbf{Between X2 and X3}}\\
	\addlinespace[1.5ex]
	\timepoint{X return the Second Armor to Dr.~Light's capsules, which proceed to upgrade it.}
	\timepoint{The maverick hunters proceed to develop a new version of Ride Armor, the DRA-00, which can change form depending on the installed module.}
	\timepoint{The maverick hunters keep fighting the mavericks. The rebellion seems to head towards its end, but mavericks keep appearing.}
	\timepoint{Repliforce is upgraded to the V2 version.}
	\timepoint{Cyber Peacock is create to defend the network from hackers.}
	\timepoint{Web Spider joins the 0th Division under Zero}
	\timepoint{Reploid scientist Dr.~Doppler discovers the cause of the maverick behavior in a computer virus he names ``Sigma Virus''.}
	\timepoint{Doppler develops a counter-measure\footnote{Depending on the source, this could be a vaccine, a cure or a suppression mechanism.} for the virus, returning infected reploids to normal.}
	\timepoint{Reploids saved by Doppler gather around him. Humans join too, and thus Doppler Town is founded.}
	\timepoint{Doppler Town is completed, and it appears to be a perfect Utopian community between reploids and humans.}
	\midrule
	\timepoint{While researching the Sigma Virus, Doppler is infected, and falls under Sigma's command.}
	\timepoint{Doppler begins developing his own army.}
	\timemoment{Vile's remains reach Doppler, who rebuild Vile as Vile mk-2. In the process, Vile is also infected with the virus, making him obsessed with revenge.}
	\timemoment{Doppler builds Bit and Byte, and creates the Nightmare Police.}
	\timemoment{In a secret laboratory, Toxic Seahorse is created.}
	\timemoment{Someone, presumably Doppler or someone under his orders, reaches and awakens Crush Crawfish, who was forgotten inside the warehouse he was sealed in.}
	\timepoint{Doppler invites to Doppler Town several advanced reploids.}
	\timemoment{Zero refuses the invitation, since he is training. He sends his second-in-command, Blast Hornet instead.}
	\timemoment{Tunnel Rhino accepts the invitation to showcase his mining skills.}
	\timepoint{Doppler put his plan in motion. The countermeasure he developed turned out to be a placebo. Cured reploids returns maverick, and a new wave of virus spreads in Doppler town, brainwashing reploids to be Doppler's soldiers. It it the beginning of the \textit{Doppler Incident}.}
	\timemoment{Blast Hornet, Blizzard Buffalo, Volt Catfish, Neon Tiger, Tunnel Rhino and maverick hunter Mac are all infected.}
	\timepoint{Infected mavericks begin rioting under Doppler's orders.}
	\timemoment{Blast Hornet is sent to guard a weapon factory and warehouse.}
	\timemoment{Blizzard Buffalo becomes incredibly aggressive, freezing a portion of Doppler Town with his powers.}
	\timemoment{Toxic seahorse is sent by Doppler to conquer the Monarch Dam, to cut off Doppler Town's water supply.}
	\timemoment{Volt Catfish, under Doppler's orders, seize Doppler's Town power plant, to redirect the electricity towards Doppler's facilities. In the process, he absorb an excessive amount of electrical power which drives him berserk.}
	\timemoment{Free again, Crush Crawfish hides in a shipyard and steals a submarine. There, he proceeds to attack and mangle anyone who draws near.}
	\timemoment{Similarly to Crawfish, Tunnel Rhino hides in a quarry, and attacks everyone who comes close.}
	\timemoment{Neon Tiger returns to the safari park he guarded. No other information are given on what he does there.}
	\timemoment{Mac returns to the Maverick Hunters HQ to work as an inside agent.}
	\timepoint{Seeing the rebellion as the chance to get his revenge, Gravity Beetle hijacks a Maverick Hunters' transport unit and flee to Doppler Town.}
	\timepoint{Beetle joins Doppler's army. The transport unit he stole is converted into an aerial fortress to move weapons.}
	\timepoint{Doppler begins collecting data about the infected reploids and starts building the \textit{ultimate battle body} for Sigma.}
	\timemoment{Simultaneously, Doppler also upgrade his body for combat.}
	%%
	% X3
	%%
	\rowcolor{Aquamarine}
	\multicolumn{2}{c}{\textbf{Mega Man X3 - The Doppler Incident}}\\
	\addlinespace[1.5ex]
	\timepoint{X and Zero are dispatched to Doppler Town to stop the rebellion and capture Doppler.}
	\timepoint{Doppler plays in advance, and sends his troop to strike the Maverick Hunters HQ. All hunter are recalled to defend their base, X and Zero included.}
	\timemoment{During the assault, Mac betrays and capture X, but is later killed by Zero, who saves his friend.}
	\timemoment{Maverick hunters repels Doppler's attack. X and Zero returns to Doppler Town to complete their mission.}
	\timepoint{X and Zero proceed facing Doppler's maverick. Doppler decides to send the Nightmare Police and Vile to pursue X as a backup plan.}
	\timemoment{Vile ignores Doppler's orders, and set up a trap by mining an abandoned factory, and waiting for X.}
	\timepoint{X faces Vile mk-2 and wins, even escaping the bombs Vile ha planted. Vile retreats within Doppler's laboratory and begins working on his next move.}
	\timepoint{Vile builds his new Ride Armor, the \textit{Goliath/Brown Bear}.}
	\timepoint{Using the D-Rex as template, scientists develop the Rex-2000 ride armor.}
	\timepoint{X and Zero stop all Doppler's mavericks, Bit and Byte included. By analyzing mavericks' control chip, Dr.~Cain discovers the location of Doppler's laboratory and also Doppler's plan to build a new body for Sigma.}
	\timemoment{X obtains from Light's capsules the third armor.}
	\timepoint{X and Zero storms Doppler's laboratory, where they face the fused form of Bit and Byte, Godkarmachine o Inary, and the press disposer, one last desperate line of defense.}
	\timepoint{X and Vile mk-2 have their last confrontation. X wins again, and Vile is killed once more.}
	\timepoint{X faces Doppler and manages to bring the doctor back to his sense. To atone for his evil actions, Doppler indicates X where Sigma is hiding.}
	\timepoint{X and Zero splits. Zero aims to destroy the laboratory's power generator, while X faces Sigma.}
	\timemoment{X and Sigma clashes once more. Despite his upgraded body, Sigma is no match for X, and his body is destroyed one more time.}
	\timemoment{In a last attempt to claim victory, Sigma enters in his viral form and corner X, in an attempt to possess his body.}
	\timemoment{Zero/Doppler appears, and saves X by using a vaccine onto Sigma, who disappears.}
	\timepoint{X and Zero teleport outside as the laboratory begins to collapse. Doppler remains inside and dies as price for the evil he had committed.}
	%%
	% X3-4
	%%
	\rowcolor{Aquamarine}
	\multicolumn{2}{c}{\textbf{Between X3 and X4}}\\
	\addlinespace[1.5ex]
	\timepoint{$1^{st}$ January 21XX: Following the failure of Doppler's project, Repliforce is reorganized in the v3 version, to improve collaboration with the Hunters and boost response time.}
	\timemoment{Web Spider moves from the Maverick Hunter 0th Division to Repliforce's guerrilla unit.}
	\timepoint{Repliforce scientists try do build the ultimate reploid by combining a peaceful heart with a proud spirit of a warrior. The experiment fail. and scientists decide to split the project into two separate being.}
	\timemoment{The peace-loving soul becomes Iris, who is sent working to the Maverick Hunters as a navigator.}
	\timemoment{The proud warrior becomes Colonel, who quickly rises in Repliforce's ranks and become General's second-hand man.}
	\timepoint{Repliforce's scientists develop the Raiden and Eagle armors, new types of Ride Armor build for combat. Later they share the projects with the Hunters.}
	\timepoint{Dr.~Cain develop the Aidion, a new type of Ride Chaser.}
	\timemoment{Repliforce somehow obtains the schematics for the Aidion and develop the Hornet, with lowered speed to make it easier to control.}
	\timepoint{The Batton Bone series is upgraded to the B81 model.}
	\timepoint{The mettaur/mettool series is upgraded to the D2 version. }
	\timepoint{Sigma manages to acquire a new body.}
	\midrule
	\timepoint{$1^{st}$ June 21XX: In an internal report, Dr.~Cain assesses Repliforce v3 performance, which failed to meet the directives. As such, the repliforce project is labeled a failure and a potential threat.}
	\timemoment{In the same report, directives for the Maverick Hunters v4 are provided}
	\timepoint{The Maverick Hunters undergo the v4 change. The 0th and 17th divisions are merged.}
	\timepoint{Sigma approaches Magma Dragoon, offering him the chance to battle X and Zero in exchange for him betraying the hunters. Dragoon accepts.}
	\timepoint{Sigma approaches General, informing him of humans' fear of Repliforce and urging him to strike first. General dismiss Sigma, refusing to betray his creators.}
	
	%%
	% X4
	%%
	
\rowcolor{Aquamarine}
\multicolumn{2}{c}{\textbf{Mega Man X4 - The Great Repliforce war}}\\
\addlinespace[1.5ex]
	\timepoint{Under Magma Dragoon order, the mechaniloid Eregion to kidnap Iris and brings her to Sky Lagoon}
	\timemoment{To save his sister, Colonel rushes to Sky Lagoon followed by Repliforce soldiers.}
	\timepoint{Magma Dragoon leads a group of maverick disguised as Repliforce soldiers to attack Sky Lagoon. He also sabotage the city's main generator.}
	\timepoint{X and Zero are dispatched to Sky Lagoon, but arrive too late and the city crashed to the ground.}
	\timepoint{X and Zero search the ruins to eliminate remaining mavericks. Here they fight and eliminate the mechaniloid Eregion.}
	\timemoment{In the process, Zero manages to rescue Iris.}
	\timepoint{Colonel and his troops arrive on the scene, but too late.}
	\timemoment{X and Zero questions Colonel and the presence of Repliforce on the scene. They ask him to disarm and follow them for interrogation. Colonel refuses and leave.}
	\timepoint{Following Colonel's refusal for interrogation, and seen the chaos provoked by troops seemingly belonging to Repliforce, the council frame Repliforce as mavericks and order their disposal.}
	\timepoint{General holds a speech to his men. He declares Repliforce will found their own independent reploid nation, and starts a coup.}
	\timemoment{Web Spider and Frost Walrus are sent to protect Reliforce's secret weapons hidden in the Jungle and North Pole respectively.}
	\timemoment{Storm Owl and Jet Stingray deploy their respective fleet to perform a diversion attack to distract the Hunters.}
	\timemoment{Slash Beast is assigned to protect the military train providing supply to Repliforce.}
	\timepoint{Repliforce begin building Final Weapon, a space station home to their new nation.}
	\timepoint{Sigma hack and reprogram Cyber Peacock to cause chaos in the cyberspace.}
	\timepoint{Sigma reactivates Split Mushroom, who turns the laboratory into a maverick stronghold.}
	\timepoint{Magma Dragoon is labeled as a maverick, having vanished after Sky Lagoon incident.}
	\timepoint{X and Zero are dispatched to stop the mavericks.}
	\timemoment{Double and Iris are assigned as X's and Zero's navigators respectively.}
	\timemoment{Magma Dragoon's hideout is found in an active volcano. X and Zero proceed to face him, discovering he was the responsible behind Sky Lagoon incident and that Repliforce was framed.}
	\timemoment{Feeling Repliforce is loosing ground, Colonel challenges X and Zero to a duel. He fights X but his defeated, while his duel with Zero is interrupted by Iris.}
	\timepoint{Final Weapon is completed, and General move inside it.}
	\timemoment{In secret, Sigma follows General.}
	\timepoint{After stopping the main mavericks activities, Maverick Hunters discover Repliforce is gathering at the Space Port and leaving. X and Zero are dispatched to stop them}
	\timemoment{Colonel remains behind to protect his men. He face the hunters and is ultimately killed.}
	\timepoint{Grieving, Iris leave the Hunters and reach for Repliforce.}
	\timepoint{The Hunters are dispatched to chase Repliforce into Final Weapon}
	\timemoment{Sigma orders Double to stop them. He proceed by killing three hunters who where ready to leave, and leave himself chasing X.}
	\timepoint{X and Zero reach Final Weapon and separate, aiming to reach General.}
	\timemoment{X meets Double, who reveals his true colors and try to kill him. He is ultimately killed, mocking X's naiveness with his last breath.}
	\timemoment{Zero meets Iris, who fuses with Colonel's core. However, the process does not work as intended, and Iris loose control. Zero is forced to fight her, but in the process he strikes fatal wound to Iris's body, who dies in Zero's arms.}
	\timepoint{X and Zero reach General and fight him.}
	\timemoment{Seeing General in trouble and the Hunters gaining ground, Sigma hijack Final Weapon's main cannon and aim it to earth. In doing so, he interrupt X and Zero from dealing General the finishing blow.}
	\timemoment{Realizing the danger, General steps back and leave the Hunters proceed forward.}
	\timepoint{X and Zero reached the main cannon and are greeted by Sigma who tries to delay them. They fight and Sigma's body is destroyed in the process. Sigma flee, having delayed the Hunters just enough for the cannon to fire.}
	\timepoint{Generals reach X and Zero. To atone for his foolishness of being Sigma's pawn, he uses his body to stop the shot. General is killed, and the explosion cause Final Weapon to start blowing up. X and Zero escape.}
\end{tabularx}
