%MEGA MAN X.TEX

\textit{Mega Man X} is born as a spin-off game of the classic Mega Man franchise for the Super Famicon/SNES consoles (later also for PC)  between the 1993 and the 1995\cite{wiki:MMX}. The game takes place one hundred years after the main franchise timeline, in a world where humans and special robots capable of having feelings co-exists and where X, one of those robots, fights the evil Sigma which aims to eliminate humans on order to have a world only for robots.

In the year 2005 a remake for PlayStation Portable was done, upgrading to a 3D graphic close to the precedent title, Mega Man X8. This game (named \textit{Maverick Hunter X }or \mhx in short) had the purpose to re-tell the first game's story with some minor changes such as X relationship with Mavericks and Sigma, which weren't present in the original game. Changes also effected level design, such as Light's capsule positions or Sigma stages, completely different from original ones.
\section[Main plot]{Main plot (X)}
In the year 21XX humans live peacefully with new kind of robots: reploids. Reploids (\ref{dict:reploids}) are particular type of robots with the ability to take autonomous decisions as well as having feelings and sentiments\cite{Xcoll1:Manual_X1}. However sometimes  a reploid' electric brain can undergo  malfunctioning making him act dangerously for nearby humans and others reploids . When this happen the reploid is labeled as ``Maverick'' and has to be stopped, in order to be repaired or disposed, by a special organization created with the exact purpose to stop mavericks: the Maverick Haunters. Leader of the Maverick Haunters is Sigma, one of the most advanced reploid of the time. 

The situation takes a turn when Sigma himself go maverick, declaring war against humanity and recruiting in its rank other maverick haunters, both willing to follow him or threatened by Sigma himself. In order to stop the war X, the main protagonist of the story, decides to joining the fight alongside Zero (a close friend of him) on the highway under attack, but is stopped by Vile, an ex-haunter released by Sigma from prison, in his ride armor. Only the intervention of Zero himself, which force Vile to flee, allow X to escape safely. The two then decide to split: while Zero goes to locate the enemy fortress, X has to deal with the threat of Sigma's mavericks. As X defeats all the eight mavericks, acquiring in the process new power-ups and strength, he joins Zero who in the meanwhile has located the Sigma fortress flying over the sea. At the entrance however they are immediately confronted with Vile and his ride armor, which first manages to capture Zero (that challenged him in a one-versus-one fight) and subsequently X too. As Vile laughs at his victory, Zero manages to escape from his cage, latches on the ride armor and detonates himself, destroying it but leaving Vile untouched. Seeing his friend's action give X new energy, allowing him to break free too and face Vile, now vulnerable, defeating him in the process. Before going on however X listens to Zero's ultimate words\cite{wiki:MMX_script}. Zero informs X that his auto-repair system cannot handle all damages taken and that X has a power even greater than his own, which makes him capable of face Sigma (eventually Zero also gives X his own Z-buster if he didn't manage to get his own buster upgrade). After that, Zero dies and X proceeds infiltrating Sigma's fortress and his dangers, including re-facing all the previously-defeated mavericks. At the end X arrives at Sigma's place where Sigma is waiting. At first Sigma acts with arrogance, looking surprised that X has managed to reach him with his only forces and claiming he could destroy him without effort. However he decides to leave the pleasure to his pet Velguarder, as he leaves the scene to assist at the fight. After X successfully manages to destroy Velguarder, Sigma changes his mind a little, understanding why Zero placed his trust in X and claiming X could have been an haunter as strong as he was. After that he proceeds to confront X, but gets defeat and his body destroyed, only his head remaining which merges with a giant wolf-based mechaniloid in the room, giving Sigma a new body to fight X. However X succeeds in destroying the new body as well, effectively getting rid of Sigma for good. As Sigma blames X for destroying his dream of a world only for reploids, Sigma himself and the fortress start to explode, forcing X to teleport to the outside. In the end X ponders about the destruction he helped to generate, on the sacrifices made for the victory, and questioning if choosing to fight was the right choice, meditating if another option was possible. As the flying fortress sinks in the ocean, X realizes that he will have to fight more battles before having the answers he needs. 
After the game's credits, it is then revealed that the next battle will not take long before occurring, since a message form Sigma is played, where the maverick states that his spirit is still intact and waiting for a new body to be built for face X again.
\section{Main Plot (\mhx)}
While being for the major part similar to the original plot, \textit{Maverick Haunter X} takes some divergence regarding characters relationship as well as X's background \cite{wiki:MM_MHX}. One of the main divergence point regard X's story prior to the war's start. Next is a summary of \textit{Maverick Haunter X} differences respect \x.

An in-depth background of the war is given, via the ``Day of $\Sigma$""\ref{App:Day_of_Sigma} OVA, explaining how Sigma started his revolution. Here X's background is also changed, now being already a Maverick Haunter (in contrast with the original, where no information are available) serving in the 17th Elite Unit alongside Zero and commanded by Sigma himself. X's haunter rank is B (in contrast to Zero's SA rank) due to his kindness and pacifist spirit, the only ones suspecting of his true potential being again Zero and Sigma. 

Another character with an expanded background is Vile. Here he aims to destroy both X and Sigma, to create his own world, hence following Sigma plans only due the fact some objectives they have match.

Last main difference regards the final portion of the story\cite{wiki:MM_MHX_script}. In fact, while in the original X and Zero immediately face Vile as they enter Sigma fortress, here X first travel through the fortress, facing previous bosses brought back to life, and only at end he meets with Zero and is stopped by Vile. As the main story, however, Vile captures both of them, resulting in Zero sacrificing and X destroying him. Finally, even Sigma has a different attitude regarding X due already suspecting X's great potential. In fact he first tests X by making him fight Velguarder (in contrast with the original game, where Sigma use Velguarder thinking to be sufficient to defeat X) and then challenges X himself, ending in the same way as the original story.	

\section{Main Characters}
\subsection{X}
X(\ref{char:X}) is the first type of a new kind of sentient robot capable of having feeling and take decision of his own developed by Dr. Thomas Light in the year 20XX. Being provided with great power, Dr. Light needed to ensure X's integrity by running a series of test which would have required thirty years to be completed. Unlikely, Dr. Light lifespan didn't allow himself to live longer to complete all tests, so he sealed X in a capsule capable of run the tests in autonomy.


In the year 21XX X's capsule is found by Dr. Cain\ref{cha:Cain} during an archaeological expedition\cite{X:Manual},\cite{wiki:Cain_journal}. Dr. Cain awakes X and, using Light's designs and X help, develop a new kind of robot later called ``Reploids''. X however remains questioning about his place in the world and the future Dr. Light wanted for him. Despite this, when the evil Sigma starts his war against human kind, X is forced to step up and fight in order to restore peace alongside his friend Zero. 


What told until now refers to the original role of X in the \x game. Nevertheless, as stated before, \textit{Maverick Haunter X} re-write X's story by providing a new background for events prior to Sigma's revolt. In this continuity Dr. light seals X away not for testing his integrity, but rather believing the world not to be ready for X's technology and potential. Here Light is firmly convinced that X has a good spirit and that he will use his power to achieve peace\cite{wiki:MM_MHX_X}. Moreover after his awakening X joins the Maverick Haunters (which do not happen in the original story), serving in the 17th Elite Unit, alongside Zero and under the direct command of Sigma. Despite having great potential, however, X's haunter rank is only B (in contrast with the SA rank of Zero) due is what seems to be his lack of decision during battle. In reality this is caused by his pacifist nature, making him reluctant to fight and preventing him to use his real power\cite{Xcoll1:Manual_X1}. Nevertheless, when the evil Sigma starts his war against human kind, X is forced to step up and fight in order to restore peace together with Zero.
\subsection{Zero}
Fighting alongside X against Sigma is Zero\ref{cha:Zero}. In the original \x game, very few information are give regarding Zero, except being a friend of X and the new leader of the Maverick Haunters\cite{X:Manual}, having the highest rank above all haunters which didn't side with Sigma. 
Different is the situation in the \mhx game, where Zero's relationship with X is explained better, the former being close friend and a mentor for X in the 17th Elite Unit, having an SA haunter rank and working under Sigma. Here it is also stated how Zero repel evil with all his strength, fighting merciless against Maverick, Sigma included\cite{Xcoll1:Manual_X1}.  

In any case, Zero story is the same for both games. He first appears at the end of the highway saving X from Vile's grasp, and asking X to take care of Sigma forces while he locates the enemy hideout. Next he's seen at the entrance of Sigma fortress where he suggests to split up, offering to act as decoy to let X sneak inside. Lastly Zero is seen for the last time at the final battle with Vile, where he sacrifices himself to destroy Vile's armor and allow X to defeat him. Finally with his last words he ask X to go and take down Sigma, eventually giving X his own Z-buster, in case X hasn't upgraded it yet.
\section{Game Mechanics}
\textit{Mega Man X}'s gameplay stays faithful to its original series by being a 2D hybrid between a run' n' gun and a platform, where the main protagonist (X in this case) has to clear different stages in order to unlock the final area of the game. Each stage has its own theme, contains a certain number of items to collect (depending on the stage it could be one ore more) which may require other power-ups to be collected first in order to be obtained (typically bosses weapons). Finally at the end of the stage a boss waits, which has to be defeat in order to clear the stage and which will give X a new weapon based on one of his attacks. As the original series all main stages can be accessed in any order and all bosses presents has a ``weak point'' corresponding to a weapon obtained from defeating one another boss first. The ``weak point'' typically consists in a weapon dealing more damage to the boss, but sometimes others effects can occur, such has stunning him or preventing him to do certain actions.

\x introduces however some new mechanics which will later define the series\cite{wiki:X1_features}:
\begin{itemize}
	\item Dash: X, via the boot parts, can dash and move faster, as well as jump higher via a dash-jump.
	\item Wall-jumping: X can jump onto wall in order to climb them or can slide down to descend slowly. He can also dash-jump off to a wall to cover a greater distance.
	\item Armor parts(\ref{X1:Armor}): By finding Light's capsules (four in total) X can be upgraded unlocking new powers which can help the player during the game.
	\item Sub-Weapon charging(\ref{X1:sub_weapon}): via the buster upgrade, X can not only charge his main X-buster, as the main series, but he can also charge his other sub-weapon to increase damage dealt or change their functionalities.
	\item Heart tanks: beside classical Sub-tank X, eight heart tank are also scattered in various stages (one per each). By picking them up X's energy grows by two, starting from 16 up to a maximum of 32\cite{stratwiki:Heart_tank}.
	\item Stage interactions: although a very limited feature, by clearing certain stages, other ones will be effected and change in some portions.
\end{itemize}
\section{Weapons}\label{X1:sub_weapon}
Here is a list of all sub-weapons available in\textit{ Mega Man X}/ \textit{Mega Man Maverick Haunter X} (\cite{MHX:manual},\cite{wiki:X_weapons}):
\subsection{Shotgun Ice}\label{Shotgun_ice}
Shotgun Ice is the weapon obtained by X after defeating Chill Penguin. It absorbs moisture in the air and fires it in crystallized form. If it hits an enemy or a hard surface, it breaks into 5 pieces which ricochet backward and get destroyed if hit another wall or enemy When charged it creates an Chill Penguin-shaped ice platform (only in \x, while in \mhx is only a sharp sled of ice) in similarly to how the boss creates his ice sculpture. X can stand on the platform which will start moving forward shortly after being created. If X creates the platform and then places himself in the same spot where the platform is creating (due the fact that the creation in not immediate) the platform will slightly push X left or right depending of its position, enabling some glitches such as wall clipping(\ref{X1:misc}, only in \x).
\subsection{Electric Spark}\label{Electric_spark}
Electric spark creates high-pressure voltage within the X-Buster and fires it, for a maximum of three at time. If the electric spark hits an hard surface, it splits in half, starting to travel up and down along the surface. The charged version of this weapon differs between the original game and his remake. In X1 upon charged X will release two electric columns in front and behind him and which will move in their respective directions, while in \mhx X will generate electricity in all directions. This weapon is acquired upon defeating Spark Mandrill.
\subsection{Rolling Shield}\label{Rolling_shield}
After beating Armored Armadillo, X will gain the Rolling Shield. By using it X spins energy at high speeds within the Buster and launches it	as an energy shot that rolls along the ground. The generated projectile is about the same size as X (half in \mhx) and will roll following the ground until making contact with an enemy or disappear after a while Only in \mhx the shield will absorb any projectile directed toward it, as well as dispose Mets even while hiding\cite{wiki:Rolling_shield}. Upon contact whit a wall, the shield will ricochet once and disappear up hitting a wall again. When charged X will surround himself with an energy field which eliminates any enemy with less than three hit points that hit it, but will disappear upon contact with enemy with more than that life value. In the original game while the charged shield is active X cannot shoot nor change weapon while in game, requiring the player to change weapon from the pause menu and thus making the shield disappear.
\subsection{Homing Torpedo}\label{Homing_torpedo}
When equipping this sub-weapon X gains the ability to fire up to two (three in \mhx)\cite{wiki:Homing_torpedo} torpedoes capable of tracking enemies. As they pick up speed, they home in on the closest enemy and pursue it. When charged X will release a fan of four (six in \mhx) fish-shaped missiles with greater speed and attack power which home better to enemies. This weapon is obtained after defeating Launch Octopus.
\subsection{Boomerang Cutter}\label{Boomerang_cutter}
The Boomerang Cutter is the weapon obtained upon defeating Boomerang Kuwanger. It fires a sharp boomerang made from a special metal. If it does not hit an enemy, it returns to its owner. and if it passes an item on its way back, it picks up the	item and delivers it to its own owner (even bringing dropped life/weapon energy from enemies). Up to three cutters can be on screen at the time\cite{wiki:Boomerang_cutter} and their trajectory will depend on the position X was when he fired them: they will arc upwards if X was standing on the ground, while they will arc downwards if X was in the air. If a boomerang successfully return to X without hitting an enemy, it will replenish the energy used to create it. Upon charged X will release four bigger boomerang spiraling out of him diagonally. In \mhx this has been changed with four boomerang of doubled size which will move back and forward in straight line a few times. 

Finally both Flame Mammoth and Launch Octopus, while not being directly weak to Boomerang Cutter, can be heavily damaged when hit with this weapon, the former loosing his trunk and the latter his tentacles, resulting in both being unable to perform certain moves.
\subsection{Chameleon Sting}\label{Chameleon_sting}
The Chameleon Sting, obtained after beating Sting Chameleon, emits a single straightforward laser which than splits into three directions: forward, up-forward, down-forward. In \mhx it instead directly emits three lasers, which can be angled diagonal-up and diagonal-down and are slightly faster. In both games the charged version makes X flash in various colors of the rainbow making him invincible to any damage (besides insta-kill hazards like pits) for a short amount of time. In the original game X cannot switch to any weapon nor shoot the current one while the invincibility is active, meanwhile in the remake is free to fire both with the current one and any other weapon\cite{wiki:Chameleon_sting}.
\subsection{Storm Tornado}\label{Storm_tornado}
The Storm Tornado turns the X-buster into a high-power fan that blasts opponents with hard-hitting wind, capable of destroying enemies that stand in its path. It shoots an horizontal tornado which stays on the screen for a short amount of time, and then starts moving in the direction X was facing when shot. Due to his length it can hit enemies multiple times, being an effective way to dispose most of them, especially bigger ones.  The \mhx version has its length halved, allowing to shoot it at a faster rate. When charged the Storm Tornado will create a large vortex covering all the screen in high, surrounding X in the original game while exploding from a shot projectile upon hitting a solid surface in the remake.\cite{wiki:Storm_tornado} It is obtained by defeating Storm Eagle.
\subsection{Fire Wave}\label{Fire_wave}
Fire Wave converts the X-buster into a powerful flamethrower, which deals continuous damage to enemies but that cannot be used underwater. Upon pressing the fire button X will start shooting fire from his X buster at a continuous rate draining energy in the process. Once charged X will fire a fireball which creates a wave of fire upon hitting the ground and moves forward for a while. However in order to charge the weapon X must keep firing, draining energy in the process. This weapon is obtained once Flame Mammoth is defeated. 
\section{First Armor}\label{X1:Armor}
While exploring stages X can run into one of the four capsules hidden by Dr. Light. When entering in contact the capsule will open revealing Dr. Light's hologram which will talk to X and give him one of the armor parts\cite{wiki:First_armor}, explaining in the process how it works.
The First Armor is composed by the following parts:
\begin{itemize}
	\item Foot Parts: Namely ``Emergency Acceleration System''\cite{X:Manual} allow X to dash forward, as well as to perform dash-jumps and wall dash-jumps as well as reducing his hitbox's height a little while dashing. Moreover X can destroy specifics blocks by wall-jumping onto them. The capsule containing the foot parts reside right in the middle of the Snow Mountain Stage, being mandatory to take. In \mhx the capsule is instead at the beginning of Factory stage.
	
	\item Body Parts: When equipped, X will have all incoming damage reduced by 50\%. It is found in the Forest stage after climbing the wall right before the cave. After defeating RT-55J the capsule will emerge from the ground. Meanwhile \textit{Maverick Haunter X} has moved it in Storm Eagle Stage, requiring the head part to access it.
	
	\item Arm Parts: Allow the X-Buster to be charged up to a third level, and to charge up special weapons. Originally Dr. Light thought this upgrade to be included in the basic X-Buster\cite{X:Manual}, bu he sealed away X when the upgrade was not ready yet, forcing him to turn it into a modification to give to X only later.
	
	Despite the capsule itself not being mandatory, the game will in any case give the player the buster upgrade in form of the Z-Buster if the player arrives at facing Vile without having found the capsule. While in \x there are no differences between the Arm Parts and the Z-Buster, in \mhx the former allow to shoot the Spiral Shot, which has the same power of the second-level charged shot but is larger and hit multiple times, while the latter deals more damage against bosses that the previous alternatives. In \textit{Meg Man X} the capsule reside in the Factory stage, requiring a precise dash-jump and the Head Parts to break some blocks in the ceiling, while in the remake it is in the same place the Body Parts was in the original game.
	
	\item Head Parts: When equipped X will gain the ability to break specific blocks with an headbutt, as well as avoid damage from falling rocks in the Forest stage. The capsule is found in the Airport stage, hidden behind an obstacle marked with a flammable warning which can be destroyed simply by shooting at it (it is not required the Fire Wave), and in Flame Mammoth stage in the remake, this time requiring the foot part to break blocks hiding it.
	
	\item Hadoken. While not being technically a component of the First Armor, rather a hidden bonus, this technique is stored too inside a Light's capsule so it is reported here. It allows X to perform the well-know technique from \textit{Street Fighter} by inputting the button combination $\downarrow$ $\searrow$ $\rightarrow$ (with X facing right) + fire button or using the same combination while X is charging and release the charged shot\cite{RTA_wiki:X1}  AND X is at full health. The projectile deals 32 point of damage\cite{wiki:Hadoken} to all enemies, basically one-shotting every non-shielded enemy, bosses included. The only exception is Sigma's final form, and only in the original \textit{Mega Man X}. 
	
	Both in the original game and its remake the capsule is hidden in Armored Armadillo Stage, see \ref{Haduken} for more information on how unlock it.
\end{itemize}
\section{Useful Techniques}
Here are listed some useful techniques which the game does not explain but can be helpful while playing\cite{RTA_wiki:X1}: %dash shot, wall dash-jump slope jump, boss charged shots
\begin{itemize}
	\item Higher jumps: If the player keep the jump button down after jumping, the reached height will be greater than the one of a simple jump.
	
	\item Wall dash-jump: With the dash upgrade, X cannot only dash and dash-jump for greater heights, but can also do it off walls, which can be very useful especially in bosses rooms to jump from a side to the other.
	
	\item Dash shots. If X shoots un uncharged shot while dashing, the projectile will deal two points of damage rather than one. This only apply for one projectile on screen at the time, so shooting multiple projectiles while dashing will give the damage boost only to the first, until it collides or exits from screen.
	
	\item Slope jumps: If X jumps while walking down a slope, he will jump higher than normal.
	
	\item Ladder wall jumps: The top every ladder, where it passes through the floor, can also act as a hole where X can wall jump. In order to do so the player has to hold left or right and press jump to leave the ladder an let X start sliding on the edge of the floor. It is also possible to do this in another manner but only for those ladder were the edge can be reached by X by jumping. To activate the ladder jump X must first start climbing the ladder and then drop down immediately, then he will be able to jump and reach the edge and start wall jumping. If X doesn't grab the ladder first, an invisible wall will stop X from grabbing the ledge and will prevent him to start wall jumping.
	
	\item Staring boss fight with a charged shot: If the player enters a boss room while holding down the fire button and a charged shot ready (any level) and release it while X is out of control, X will it shoot immediately as the boss fight starts.
\end{itemize}

\section{Highway Stage}
The Highway Stage (Central HighWay in \mhx) is the first stage of the game. X arrives here in order to join the fight against Sigma's forces. The stage is rather straightforward, having X to travel while eliminating different enemies, while also teaching the player some basic mechanics such as wall-jumping.  The stage can be split into two main sections\cite{stratwiki:HighWay}, the second one having more gaps and pieces of the highway falling as X stands on (recognizable by a darker texture color). In the first section of the highway two sub-bosses are presents in form of Bee Bladers\ref{minibossBee_Bladers}. At the end of the stage X will be attacked by Death Rogumer, which will start sending towards him several Road Attackers(\ref{enem:Road_attackers}). Once some of them have been destroyed, Vile will drop out the airship and start attacking X with his ride armor. Vile is literally invincible, so there is no point in fighting. Instead as X drop below a certain amount of energy Vile will start shooting an energy projectile toward X and has soon as it connects, X gets trapped and the fight ends, starting the cutscene with Zero saving X. A common speedrun  technique involve having X getting hurt in order to start the boss fight with low health, which will force Vile to shoot the trapping projectile and then run into it, basically skipping the entire fight. Attention however has to be made, since Vile will not stop attacking with the armor, which may results in the player being defeated.

This stage contains following enemies\cite{wiki:Highway}:
\begin{itemize}
	\item \hyperlink{enem:Ball_De_Voux}{Ball De Voux }
	\item \hyperlink{enem:Bomb_Been}{Bomb Been }
	\item \hyperlink{enem:Crusher}{Crusher }
	\item \hyperlink{enem:Gun_Volt}{Gun Volt}
	\item \hyperlink{enem:Jamminger}{Jamminger}
	\item \hyperlink{enem:Road_Attackers}{Road Attackers }
	\item \hyperlink{enem:Spiky}{Spiky }
	\item \hyperlink{miniboss:Bee_Blader}{Bee Blader }
\end{itemize}
 
\section{Ocean}
The \textit{Ocean stage} (later renamed Subterranean Base in \mhx) is where Launch Octopus hides himself. Here X starts from the shoreline to immerse short after the beginning of the level. Once underwater X will jump higher than normal which, combined with the dash-jump and the beginning of the level being placed on top of a cliff, make the player capable of skipping a good portion of the first part of the underwater scenario\cite{stratwiki:Ocean}. Various fish-based enemies are present, but main difficulties of the sub-bosses the stage has, being three plus an optional one. In the first part main difficulties are given by spiked pit which X has to jump and from where Sea Attacker will spawn in group of three, interrupting X's jump and making him fall into the pit, and from the two Angler sub bosses, the second one being particular dangerous, since the floor has two spiked pits and the Angler will keep using his vacuum attack to push/pull X into them. Here the best strategy consists in stay at the leftmost platform and keep shooting, dashing to the right once it start pulling and shooting while it pushes X. Other than that Anglers will also shoot X four serpent-shaped harpoon which will move horizontally and then fall onto X when they're above him. Finally Anglers will rarely shoot a beam of light from their lamp, which can also be destroyed. After passing the second sub-boss the second part of the stage begins. Here spiked gaps are rarer (although still present) and whirlpools will start to appear at regular intervals and in specific positions. Those whirlpools can be used to propel X up to the ocean's surface. Proceeding in the stage bombs will start dropping from above, fired by a Cruiziler enemy. X can either climb a whirlpool to get onto it and destroy its core, making it sink and stop it from shooting bombs, or avoiding it and proceed in the level. Once passed falling bombs, X will find himself into an arena filled with sand. Here an Utuboros will start attacking him, rising from the sand, than swimming for a while and then immerse again in the sand. It is invincible for most of its body (which X can stand on), only the head and tail being vulnerable. Although its weakness is considered to be the Boomerang Cutter, due to lack of invincibility frame a single Storm Tornado fired behind its head will destroy him in one shot\cite{wiki:Utuboros}. After this other sub-boss X will have go on only for a little before finding himself in front of the boss door.
Following enemies are present in the stage\cite{wiki:Ocean}:
\begin{itemize}
	\item \hyperlink{enem:Amenhopper}{Amenhopper}
	\item \hyperlink{miniboss:Anglerge}{Anglerge}
	\item \hyperlink{enem:Gulpfer}{Gulpfer }
	\item \hyperlink{enem:Cruiziler}{Cruiziler}
	\item \hyperlink{enem:Mega_Tortoise}{Mega Tortoise }
	\item \hyperlink{enem:Sea_Attacker}{Sea Attacker}
	\item \hyperlink{enem:Sky_Claw}{Sky Claw }
	\item \hyperlink{miniboss:Utuboros}{Utuboros }
\end{itemize}
\subsection{Heart Tank}
This stage only has an heart tank has collectible. In order to get it the player must first destroy the Cruizer by reaching the ocean's surface via a whirlpool, then climbing on it and then shoot at its blue core, avoiding the Sky Claws which the ship will spawn. Once destroyed the Cruizer will sink and will destroy the ocean floor, revealing an hidden portion with a large room filled with spiked gaps on the ground. Here another Utuboros (technically the first since the other reside later in the level) must be defeated, in order to open the door which leads to an Heart Tank. After that X must exit from where he entered and climb the wall where the ship fall in order to return to the main path.
\subsection{Launch Octopus}
Launch Octopus, the ``\textit{Armament General of the Deep Sea}''\cite{wayback:X_resources} (or ``\textit{Military general of the deep}''\cite{MHX:manual} in \mhx) was a Maverick Haunter of the 6th fleet armada before joining Sigma's rebellion and setting his base in the dept of the Ocean, in order to attack marine cities with his army of mechaniloids and to cut off shipping routes. In \x he joins Sigma due the fact he shares the dream of a world only for reploids, having always had doubt on protecting humans, while in \mhx he is pictured military tactician which want to achieve beauty in combat, considering himself an unappreciated artist of underwater fighting. Only Sigma understand his art, making Launch Octopus side with him\cite{wiki:MM_MHX_script}.

In battle Octopus has two main techniques: Homing torpedo and Energy Drain. In reality he has a third technique, which consists in firing what can be considered a charged version of his Homing Torpedo. Both his types of missiles can be destroyed by shooting at them. Launch Octopus will always start the boss fight with a barrage of homing missile, to than switch to one of the other two weapons he has. Just like X, Octopus can fire a charged version of his homing missiles, which are piranha-shaped and homes much faster than their counterpart. Finally he has his Energy Drain attack. When performing this Octopus will first swim on top of the arena, either left or right, and then start spinning to create a whirlpool to suck X in. If he succeed he will start draining X energy to replenish his own, prolonging the fight. Octopus main weakness is the Rolling Shield, which deals him extra damage but can be hard to hit, due Octopus high mobility and the shield colliding with his missiles instead. However Octopus can be also heavily damaged by the Boomerang Cutter, which in three hits will sever his tentacles blocking him to perform his Energy Drain attack. 

Officially\cite{wayback:X_resources} Launch Octopus is 232 cm tall and 182 Kg heavy, in contrast with in-game information\cite{wiki:Launch_Octopus} which show a weight value smaller than the actual one (see fig \ref{Octopus_specs}).

One Launch Octopus has been defeated X will gain the Homing Torpedo(\ref{Homing_torpedo}) weapon, as well as cause a flood in the Forest Stage, making water appear near the beginning of the stage.
\section{Snow Mountain}
\textit{Snow Mountain}(\textit{Abandoned Missile Base in \mhx}) is probably the first stage most people go when starting the game, due to its low level of danger it contains\cite{stratwiki:Snow_mountain}, as for having inside the most useful upgrade X get can get, the Foot Parts. The stage, as the name states, takes place in a snow-covered mountain which X has to climb to get to the boss. The stage is divided into three main areas. The first area is where X starts and consists in a path that brings him inside a cave through a series of enemies. Once inside the cave (the second area) X has first to climb it by following a zig-zag path while also avoiding enemies which drop from higher level, and then to surpass some iced platform separated by pits until he reaches the end of the cave. In the third area X is again on the outside. Here he can take a Ride Armor and proceed for a while. With the armor X can also destroy the igloo he finds and that would otherwise start spawning enemies. Passed the first igloo the player can make a choice: he could either keep the Ride Armor and enter the small cave which comes next, where he has to jump some gaps using the armor while also face another enemy Ride Armor, or use his own armor to reach the top of the cave (jumping out of the armor to gain extra lift), basically skipping the lower portion. After that section X meets a tall wall which the armor cannot surpass, forcing him to leave it behind. Here he has to following a path full of slopes, gaps and Snow Shooters, which will throw snowballs at him and that become bigger the longer they roll on the snowy ground. After passing these enemies, the player will reach the boss door.

The stage contains following enemies\cite{wiki:Snow_mountain}:
\begin{itemize}
	\item \hyperlink{enem:Armor_Soldier}{Armor Soldier} (with Ride Armor)
	\item \hyperlink{enem:Axe_Max}{Axe Max}
	\item \hyperlink{enem:Bat_Bone}{Bat Bone}
	\item \hyperlink{enem:Bomb_Been}{Bomb Been}
	\item \hyperlink{enem:Flammingle}{Flammingle}
	\item \hyperlink{enem:Jamminger}{Jamminger }
	\item \hyperlink{enem:Ray_Bit}{Ray Bit}
	\item \hyperlink{enem:Snow_Shooter}{Snow Shooter}
	\item \hyperlink{enem:Spiky}{Spiky}
	\item \hyperlink{enem:Tombot}{Tombot}
\end{itemize}
\subsection{Foot Parts}
This stage contains the Armor capsule for the Foot Parts, which allows X to dash, moving faster, perform dash-jumps and wall dash-jumps and alse reducing a little the height of this hitbox. The capsule is found on directly path after having climbed the first part of the cave. Since it is right in the middle of the path it is not avoidable, making it the only mandatory capsule of the entire series.
\subsection{Heart Tank}
The Heart Tank of this stage is hidden in the last igloo X meet before facing the section with snow balls. To reach it X has to jump using the Ride Armor. Right after the first igloo there is a light blue column, right before the cave with the enemy Ride Armor. From the top of the column the player has to jump with the armor and, once reached the maximum height, jump out of it in order to reach the wall which brings to the upper path. Here two other igloo are found which can be destroyed, now that the armor is gone, by using the Fire Wave weapon. In particular the last one contains the searched Heart Tank.
\subsection{Chill Penguin}\label{boss:Chill_Penguin}
The ''\textit{Lord of the Snowy Plains}`` (''\textit{Emperor of the Snowfield}``\cite{wayback:X_resources}), better known as Chill Penguin was a reploid of the 13th Polar Division, specifically designed for operating in polar environments also tanks to his small-size body. However due to the long permanence in the South Pole, away from civilization, Chill Penguin grown tired of his mission, seeking a way to get away from there. Sigma's rebellion give him exactly what he needed to get away, allowing him to escape and join Sigma in his fight. There are however some differences in how his story is told between \x and \textit{Maverick Haunter X}. In the former, after Sigma starts his revolt, Chill Penguin autonomously eliminated his own commander and escaped to join Sigma while also returning to the civilization\cite{Xcoll1:Manual_X1}. Once arrived Chill Penguin seized a mountain base in order to crush nearby cities using avalanches. Meanwhile in the remake it is Sigma himself which took away Chill Penguin from the South Pole by making him join the 17th division together with X and Zero, even before the revolution's beginning\cite{MHX:manual}. Later, while facing X, Chill Penguin revealed that, beside leaving the South Pole, he also joined the revolt due the payment Sigma gave him\cite{wiki:MMX_script}. Another minor difference with the original version is that, in the remake, Chill Penguin seized an abandoned missile base, hinting his purpose was to use it to attack the cities. He's known to be a belligerent, rowdy (sometimes even warped) individual, while also having trouble with his partner Flame Mammoth (\ref{boss:Flame_mammoth}) due his jealously of Mammoth size and the latter attitude of bullying smaller reploids.

Chill Penguin is often considered the easiest boss of the game and the first one a player must face due the simplicity of avoiding his attacks, also thanks to the Foot Parts the stage give to the player. He has four main attack which will perform at random\cite{wiki:Chill_Penguin}. When he use his Shotgun Ice, Chill Penguin will shot four frozen projectiles which travel in a straight line, although some of them can fall off and slide on the ground, which shatter upon contact with a wall but can nullify X shot if the two met. Other times instead of his projectiles he will emit snow which will create two penguin-shaped ice sculpture and, if X is in range, will also freeze him in place. Sculptures act both as obstacles (X takes damage if he makes contact with them) and as cover since both X and Chill Penguin projectiles will be stopped by them. However X shots can damage and eventually break them. In some occasion Chill Penguin will leap in the air and grab the hook on the ceiling, unleashing a blizzard which will push X and the statues (if present) against a wall. When the sculpture hit a wall they shatter. Finally he can also slide on the floor for a while, turning immediately in case he hits a wall. While in this state he is invincible, but will also get rid the sculpture he creates.  As it is possible to see, Chill Penguins attacks only cover the low part of the arena, meaning the best strategy to fight him consist in staying on the higher part via continuous wall-jumps, only dropping to hit him when possible. Attention however must be made, since sometimes Chill Penguin will perform a high jump toward X position which can hit him even if he's  in the high corner of the room. Beside that he can be hit at any times, even when grabbing the hook, beside when sliding. He's weakness is the Fire Wave, which will burn and stun him for a while, but it has no other particular effect.

After defeating him X will gain the Shotgun Ice(\ref{Shotgun_ice}) weapon as well as freezing the lava in the Factory Stage, considerably reducing the danger level of the stage.

\section{Gallery}
The Gallery Stage (or Energy Mines Ruins in \mhx) is the stage where controlled by Armored Armadillo. Peculiarity of this level are its mine cart which X can stand and, as soon as he does it, they start moving following the track, increasing their speed as they keep going and destroying all enemies that enter in contact with it. Hoever the player must be careful, as all the carts end their run into pits, bringing X down with them if he doesn't jump off at the right moment. This stage is also famous for containing the secret Light's capsule which teach X the Haduken technique.

The stage itself is rather simple. Immediately at the beginning a mine cart is present which brings the player forward in the level taking care of enemies for him, but that end its ride when it comes across a series of gaps, one of which it cannot jump and falls into. For that moment the player must have dismount from the cart. After this sequence only few small gaps and some enemies separate X from the next section, which begin when he has to fall off a long pit in the ground. Here as he touches the floor a Mole Borer will destroy the left wall and start chasing X. It is invincible and its roller can insta-kill X if he touches it. Here only two solutions are possible: the first one is to escape to the right, continuing in the level; the second one is, as soon as X reaches the ground, wall jump immediately to the left before the Mole Borer breaks the wall and then jump down, following it from behind (while also gaining acces to the sub tank). In both cases the player has to go right to continue, followed by the mechaniloid (which will eventually crash and explode) or not. After this section another mine cart waits, which will bring the player deeper in the level and, again, end its ride into a pit. Just like the before after this part another large hole in the ground is present and X has to fall off to proceed, meeting another Mole Borer one he lands. This time however he will land behind it, avoiding another chase and, on the other hand, allow the mechanilod to create a passage for the player, until it crashes and explodes again (the player may also want to destroy it to avoid since while going it also destroys the acces to the heart tank) . Here there is the final cart X has to take to proceed. This mine cart brings X through many enemies until it reaches an opening on the mountain and flies off over a huge gap, impossible for X to jump. Once in the air the player must jump off the cart in order to land on the other side of the pit (or grab the wall if high enough), where the boss door is. While riding in the final parts a group of mechanical birds enemies will start spawning and fly alongside X. Since they fly the cart cannot destroy them, but X will have to, since they can mess up the final jump by hitting him and making him fall into the pit.

Following enemies are present in the stage\cite{wiki:Gallery}
\begin{itemize}
	\item \hyperlink{enem:Bat_Bone}{Bat Bone} 
	\item \hyperlink{enem:Batton_M-501}{Batton M-501} 
	\item \hyperlink{enem:Dig_Labour}{Dig Labour} 
	\item \hyperlink{enem:Flammingle}{Flammingle} 
	\item \hyperlink{enem:Metal_Wing}{Metal Wing} 
	\item \hyperlink{enem:Metall_C-15}{Metall C-15} 
	\item \hyperlink{miniboss:Mole Borer}{Mole Borer}
	\item \hyperlink{enem:Spiky}{Spiky}
\end{itemize}
\subsection{Sub Tank}
The Sub Tank is located where the first Mole Borer spawn. In order to get it the player has, once arrived to the firs big gap in the ground, jump into it and then immediately wall-jump to the left, in order to let the Mole Borer break the wall and go right passing under X. Once it is passed, the player can safely jump off and go left to find the sub tank where the Mole Borer originally was. 
\subsection{Heart Tank}
The heart tank is located near where the second Mole Borer is found. Once the player jumps off the gap he has to chase the mechaniloid and destroy it in time, since as he proceed it destroy the walls which allow to access the Heart Tank. To do this the Fire Wave weapon is suggested, since it deals massive amount of damage to it a short span. 
\subsection{Haduken}\label{Haduken}

\section{Factory}
\section{Airport}
\section{Tower}
\section{Power Plant}
\section{Forest}
\section{Sigma Stage (1-4)}
\section{Miscellaneous}\label{X1:misc} %wall clip glithc, seven pixel, flying hadoken